\thetitle

### 2008-11-04 paper.tex
Corrections to the proof text.

Having defined our representation of network behavior and presented the procedure for stochastically generating workload, we turn to deriving useful expressions for commonly used network properties in terms of these algebraic building blocks.

@@

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The row vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\smallfrac{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\ones = \mat{V}\ones \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\ones}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\ones} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\ones.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vectors, as it does in Matlab.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{conditionality} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether they make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

@@

In more sophisticated modeling work, where uniformity is discarded as too simple a model for behavior, marginality is often applied instead. It is assumed---often implicitly---that marginal models are adequate to capture the essential aspects of network behavior. We put that implicit assumption to the test here. How well do perfect marginal models represent real behavior? When we say that our marginal models are ``perfect,'' we mean that they are nonparametric and calculated directly from trace behavior. These are the marginal models that most accurately describe the trace traffic, because they are directly derived from it and make no parametric simplifications. This provides an upper bound on the quality of marginal models in general, since parametric marginal models are derived, in turn, as simplifications of these nonparametric marginal behaviors. \Table{traffic-models} provides a complete list of all the traffic models we compare in our evaluation.

@@

Another potential concern about generality is the relatively limited set of performance metrics evaluated.
As mentioned in \Section{performance-metrics}, we have evaluated a broad variety of performance metrics---28 in all.
The metrics evaluated here were selected both because they are among the most commonly used in evaluations, and because they are representative of the results for other metrics.
In general, metrics at the same level of the protocol stack tend to behave in related ways:
they may be positively or negatively correlated, but if one metric is severely distorted, it is unlikely that others are left intact.
The direction of the distortion of metrics is highly sensitive to the experimental setup;
the presence of error, however, is not.
In other words, models that are sufficiently realistic in one experimental setup tend to be sufficiently realistic in other experiments;
models that misrepresent performance metrics in certain cases tend to do so in other cases as well.
The direction of the distortion may change, but the fact that they are inaccurate does not.
See previous work using the same technique for evaluating realism for further examples with different experimental conditions and sets of performance metrics considered~\cite{Karpinski07:realism,Karpinski07:cbr-failure}.

@@

A related issue is the significant simulation time incurred when experiments use realistic volumes of traffic.
Indeed, this is a problem:
we have run our simulations on a 64-node Itanium cluster, and the experiments still take weeks to complete.
Given the current state of the art in simulators and \caps{CPU} power, however, this problem is unavoidable.
Including model preparation times, running simulations with uniform or marginal models takes negligibly less time than running simulations using realistic models like the \caps{GMM}.
One of the possible effects of this research, however, may be the ability to classify and catalog an realistic set of ``exemplary'' traffic scenarios for various applications.
Such a catalog is far from existing, but its existence would allow researchers to run far fewer simulations to achieve incomparably more general and reliable results.

@@

It remains to show how we can simplify and reduce the representation of network behaviors without making unwarranted and manifestly false assumptions of uniformity or marginality of network behaviors.
In \Section{modeling-concepts}, we observed that application of uniformity and marginality assumptions to traffic instances is equivalent, in the \caps{GMM}, to right and left multiplication, respectively, by matrices of rank one. These transformations destroy almost all of the information in the original traffic matrix.
Conditional models are equivalent to left-multiplication by somewhat less degenerate matrices, but they achieve realism only by approaching the \caps{GMM} itself.
In this section we describe matrix factorization, which provides an approximate low-rank representation of the original traffic.
This technique not only allows us to model and analyze traffic without destroying the information content, but also leads us to a deep analytical understanding of network behaviors that matches our intuitive understanding of typical modes of network behavior.

We present here preliminary results from applying nonnegative matrix factorization (\caps{NMF}) to the packet behaviors of real flows. Recall from \Section{general-matrix-model} that the matrices $\mat{Z}$ and $\mat{V}$ represent the packet size and inter-packet interval histograms of a collection of flows.
We apply \caps{NMF} to the concatenation of these matrices, $\mat{P}=[\mat{Z}~\mat{V}] \in \R^{f \times (d_z+d_v)}$. \caps{NMF} attempts to approximate $\mat{P}$ as the product of nonnegative matrices:
\begin{align}
\mat{P} \approx \mat{W}\mat{\Sigma}\mat{H},
\end{align}
where $\mat{W} \in \R^{f \times b}$ and $\mat{H} \in \R^{b \times (d_z+d_v)}$ are both row-stochastic, while
$\mat{\Sigma} \in \R^{b \times b}$ is diagonal with descending diagonal entries.
$b\in\N$ is the rank of this factorization, which must be determined somehow as well.
What is the interpretation of such a factorization?
The rows of $\mat{H}$ are \emph{basic behaviors}---pairs of packet size and inter-packet interval distributions, such that each flow's packet behavior can be approximated as a linear combination of these basic behaviors.
Specifically, the matrix $\mat{M}\mat{\Sigma}$ gives the mixing coefficients for each flow.
The diagonal entries of $\mat{\Sigma}$ have a special meaning as well:
they are the number of packets associated with each basic behavior.
Thus the basic behaviors are sorted in descending order of how much traffic they explain.
% Note that the factorization does not associate basic behaviors with individual packets;
% rather, total flow behavior is explained as a mixture of basic behaviors, so the fraction of packets in each flow explained by a given behavior is known, while the specific packets are unknown.

The striking results of applying nonnegative matrix factorization to $\mat{P}$ are shown in \Figure{basic-behaviors}. Twelve basic behaviors suffice to explain all the traffic in a ``toy''  sample of 4138 flows. The pairs of packet size and inter-packet interval distributions are almost immediately recognizable as resembling intuitive modes of network behavior. The first basic behavior, for example has all packets near the \caps{MTU}, while intervals are smoothly distributed around a fraction of a millisecond. This is what we would expect from downloading large files; and indeed, the breakdown of packets by port number bears out this interpretation---almost all of the traffic is \caps{HTTP} server traffic, with small slivers of \caps{IMAP} and \caps{SSH} server traffic. The second basic behavior is equally intuitive: tiny packets with frequency distributed around 0.1 seconds---this is all interactive \caps{SSH} traffic, as indicated by the associate pie chart.
The other behaviors are listed in \Table{basic-behaviors} with interpretations.
% This is precisely the behavior we expect from interacting with a remote terminal via keystrokes and screen updates.
The true significance of this result lies in the fact that \caps{NMF} succeeds in classifying flows by network behavior completely automatically, not only without using port numbers, but also without \emph{any} information about the number or kind of plausible interpretations.´
The algorithm not only agrees with our intuition about network behavior, but exceeds it by discovering real but unknown behaviors awaiting interpretation.

@@

We have presented a fundamentally new, algebraic way of representing traffic patterns in local area networks. We call this representation the general matrix model. Each flow of a traffic collection is represented as a single high-dimensional vector with components representing the \caps{IP} protocol type, source and destination nodes, start time, flow size, and packet behavior. The essential property of the algebraic representation is that standard vector operations compute natural and useful descriptions of aggregate behavior over the collection of flows represented. Our experimental validation demonstrates clearly that the general matrix model accurately reproduces the performance characteristics of of real traffic.

The benefits of a performance-preserving algebraic representation are multifold. The algebraic forms of the simplifying assumptions made by many common modeling approaches provide unprecedented clarity and coherence to a complex and confusing subject. For example, assumptions that various aspects of flow behavior are stochastically or deterministically uniform all take the same form algebraically: left matrix multiplication. The other major class of common simplifying assumptions made by traffic models is to apply some marginal behavior across the entire collection of flows or to disjoint subsets of the flows. Such simplifications correspond to right matrix multiplication in \caps{GMM}. Because of the simplicity and clarity that the algebraic structure brings to the subject, we can see clearly now that both common types of simplifying assumptions are na\"ive and simplistic. Our experimental results bolster this conclusion: both uniform and marginal models significantly misrepresent many important network performance metrics. With the general matrix model, however, we stand poised to use the powerful tools of modern linear algebra to develop general, elegant and effective models of network behavior.

>>>>

Having defined a specific matrix representation of network behavior,
% and a procedure for stochastically generating workload from a given matrix,
we turn now to deriving useful expressions for commonly used network properties in terms of these algebraic building blocks.

@@

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The row vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each matrix column represents, whether size or interval.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\smallfrac{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\ones = \mat{V}\ones \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\ones}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\ones} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\ones.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vectors, as it does in Matlab.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniform}, \textit{marginal}, and \textit{conditional} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether they make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

@@

In more sophisticated modeling work, where uniformity is discarded as too simple a model for behavior, marginality is often applied instead. It is assumed---often implicitly---that marginal models are adequate to capture the essential aspects of network behavior. We put that implicit assumption to the test here. How well do perfect marginal models represent real behavior? When we say that our marginal models are ``perfect,'' we mean that they are nonparametric and calculated directly from trace behavior. These are the marginal models that most accurately describe the trace traffic, because they are directly derived from it and make no parametric approximations. This provides an upper bound on the quality of marginal models in general, since parametric marginal models are derived, in turn, as simplifications of these nonparametric marginal behaviors. \Table{traffic-models} provides a complete list of all the traffic models we compare in our evaluation.

@@

Another potential concern about generality is the relatively limited set of performance metrics evaluated.
As mentioned in \Section{performance-metrics}, we have evaluated a broad variety of performance metrics---28 in all.
The metrics evaluated here were selected both because they are among the most commonly used in evaluations, and because they are representative of the results for other metrics.
In general, metrics at the same level of the protocol stack tend to behave in related ways:
they may be positively or negatively correlated, but if one metric is severely distorted, it is unlikely that others are left intact.
The direction of the distortion of metrics is highly sensitive to the experimental setup;
the presence of error, however, is not.
In other words, models that are sufficiently realistic in one experimental setup tend to be sufficiently realistic in other experiments;
models that misrepresent performance metrics in certain cases tend to do so in other cases as well.
The direction of the distortion may change, but the presence or absence of accuracy does not.
See previous work using the same technique for evaluating realism for further examples with different experimental conditions and more performance metrics considered~\cite{Karpinski07:realism,Karpinski07:cbr-failure}.

@@

A related issue is the significant simulation time incurred when experiments use realistic volumes of traffic.
Indeed, this is a problem:
we have run our simulations on a 64-node Itanium cluster, and the experiments still take weeks to complete.
Given the current state of the art in simulators and \caps{CPU} power, however, this problem is unavoidable.
Including model preparation times, running simulations with uniform or marginal models takes negligibly less time than running simulations using realistic models like the \caps{GMM}.
One of the possible effects of this research, however, may be the ability to classify and catalog a realistic set of ``exemplary'' traffic scenarios for various applications.
Such a catalog is far from existing, but its existence would allow researchers to run far fewer simulations to achieve incomparably more general and reliable results.

@@

It remains to show how we can simplify and reduce the representation of network behaviors without making unwarranted and manifestly false assumptions of uniformity or marginality of network behaviors.
In \Section{modeling-concepts}, we observed that application of uniformity and marginality assumptions to traffic instances is equivalent, in the \caps{GMM}, to right and left multiplication, respectively, by matrices of rank one. These transformations destroy almost all of the information in the original traffic matrix.
Conditional models are equivalent to left-multiplication by somewhat less degenerate matrices, but they achieve realism only by approaching the \caps{GMM} itself.
In this section we describe a matrix factorization technique that can provide an approximate low-rank representation of the original traffic without assuming uniformity or marginality.
This technique not only allows us to simplify and analyze traffic without destroying the information content, but also leads us to a deep analytical understanding of network behaviors that matches our intuitive understanding of typical modes of network behavior.

We present here preliminary results from applying nonnegative matrix factorization (\caps{NMF}) to the packet behaviors of real flows. Recall from \Section{general-matrix-model} that the matrices $\mat{Z}$ and $\mat{V}$ represent the packet size and inter-packet interval histograms of a collection of flows.
We apply \caps{NMF} to the concatenation of these matrices, $\mat{P}=[\mat{Z}~\mat{V}] \in \R^{f \times (d_z+d_v)}$. \caps{NMF} attempts to approximate $\mat{P}$ as the product of nonnegative matrices:
\begin{align}
\mat{P} \approx \mat{W}\mat{\Sigma}\mat{H},
\end{align}
$\mat{W} \in \R^{f \times b}$ is column-stochastic, $\mat{\Sigma} \in \R^{b \times b}$ is diagonal with descending diagonal entries, and $\mat{H} \in \R^{b \times (d_z+d_v)}$ is row-stochastic.
The inner dimension, $b\in\N$, must be determined as well.
What is the interpretation of such a factorization?
The rows of $\mat{H}$ are \emph{basic behaviors}---pairs of packet size and inter-packet interval distributions, such that each flow's packet behavior can be approximated as a linear combination of these basic behaviors.
Specifically, the matrix $\mat{M}\mat{\Sigma}$ gives the mixing coefficients for each flow.
The diagonal entries of $\mat{\Sigma}$ have a special meaning as well:
they are the number of packets associated with each basic behavior.
Thus the basic behaviors are sorted in descending order of how much traffic they explain.
% Note that the factorization does not associate basic behaviors with individual packets;
% rather, total flow behavior is explained as a mixture of basic behaviors, so the fraction of packets in each flow explained by a given behavior is known, while the specific packets are unknown.

The striking results of applying nonnegative matrix factorization to $\mat{P}$ are shown in \Figure{basic-behaviors}. Twelve basic behaviors suffice to explain all the traffic in a ``toy''  sample of 4138 flows. The pairs of packet size and inter-packet interval distributions are readily recognizable as resembling intuitive modes of network behavior. The first basic behavior, for example, has all packet sizes near the \caps{MTU}, while intervals are smoothly distributed around a fraction of a millisecond. This is what we would expect from downloading large files; and indeed, the breakdown of packets by port number bears out this interpretation---almost all of the traffic is \caps{HTTP} server traffic, with small slivers of \caps{IMAP} and \caps{SSH} server traffic. The second basic behavior is equally intuitive: tiny packets with frequency distributed around 0.1 seconds---this is all interactive \caps{SSH} traffic, as indicated by the associate pie chart.
The other behaviors are listed in \Table{basic-behaviors} with interpretations.
% This is precisely the behavior we expect from interacting with a remote terminal via keystrokes and screen updates.
The true significance of this result lies in the fact that \caps{NMF} succeeds in classifying flows by network behavior completely automatically, not only without using port numbers, but also without \emph{any} information about the number or kind of plausible interpretations.´
The algorithm not only agrees with our intuition about network behavior, but exceeds it by discovering real but unknown behaviors awaiting interpretation.

@@

We have presented a fundamentally new, algebraic way of representing traffic patterns in local area networks. We call this representation the general matrix model. Each flow of a traffic collection is represented as a single high-dimensional vector with components representing the \caps{IP} protocol type, source and destination nodes, start time, flow size, and packet behavior. The essential property of the algebraic representation is that standard vector operations compute natural and useful descriptions of aggregate behavior over the collection of flows represented. Our experimental validation demonstrates that the general matrix model accurately reproduces performance characteristics of of real traffic.

The benefits of a performance-preserving algebraic representation are multifold. The algebraic forms of the simplifying assumptions made by many common modeling approaches provide unprecedented clarity and coherence to a complex and confusing subject. For example, assumptions that various aspects of flow behavior are stochastically or deterministically uniform all take the same form algebraically: left matrix multiplication. The other major class of common simplifying assumptions made by traffic models is to apply some marginal behavior across the entire collection of flows or to disjoint subsets of the flows. Such simplifications correspond to right matrix multiplication in \caps{GMM}. Because of the simplicity and clarity that the algebraic structure brings to the subject, we can see that both common types of simplifying assumptions are na\"ive and simplistic. Our experimental results bolster this conclusion: both uniform and marginal models significantly misrepresent many important network performance metrics. With the general matrix model, however, we stand poised to use the powerful tools of modern linear algebra to develop general, elegant and effective models of network behavior.

### 2008-11-04 tables/traffic_models.tex
Corrections to the proof text.

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}' = (\nicefrac{1}{n})\,\mat{A}\ones$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}' = (\nicefrac{1}{n})\,\mat{S}\ones \quad
 \mat{D}' = (\nicefrac{1}{n})\,\mat{D}\ones$ &
all nodes equally likely as source or destination
\\\hline
full uniform &
\textit{all uniform transformations} &
all start times, sources and destinations equally likely
\\\hline\hline
time marginal &
$\mat{A}' = (\nicefrac{1}{f})\,\ones\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}' = (\nicefrac{1}{f})\,\ones\mat{B}$ &
flow size (bytes) is chosen independently of other properties
\\\hline
node marginal &
$\mat{S}' = (\nicefrac{1}{f})\,\ones\mat{S} \quad
 \mat{D}' = (\nicefrac{1}{f})\,\ones\mat{D}$ &
nodes behave distinctly, but behavior is independent of flows
\\\hline
packet marginal &
$\mat{Z}' = (\nicefrac{1}{f})\,\ones\mat{Z} \quad
 \mat{V}' = (\nicefrac{1}{f})\,\ones\mat{V}$ &
packet behavior is variable bit-rate, aggregated across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}' = \rStoch(\trans{\mat{S}}\mat{S})\,\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest. conditional &
$\mat{F}' = \rStoch(\trans{\mat{D}}\mat{D})\,\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
% mixed conditional &
% $\mat{F}' = \nicefrac{1}{2}\,(
%               \rStoch(\trans{\mat{S}}\mat{S}) +
%               \rStoch(\trans{\mat{D}}\mat{D})
%             )\,\mat{F}$ &
% flow behaviors are aggregated on a mixed source/destination basis
% \\\hline
\end{tabular}
\caption{Matrix-based traffic models evaluated by paired differential simulation.}
\label{tab:traffic-models}
\end{center}
\vspace{-1em}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\small
\begin{tabular}{|c|c|l|}
\multicolumn{1}{c}{\textbf{model}} &
\multicolumn{1}{c}{\textbf{transformation}} &
\multicolumn{1}{c}{\textbf{description}} \\
\hline
\caps{GMM} &
--- &
the general matrix model
\\\hline\hline
time uniform &
$\mat{A}' = (\nicefrac{1}{n})\,\mat{A}\ones$ &
all start times are equally likely
\\\hline
node uniform &
$\mat{S}' = (\nicefrac{1}{n})\,\mat{S}\ones \quad
 \mat{D}' = (\nicefrac{1}{n})\,\mat{D}\ones$ &
all nodes are equally likely as source or destination
\\\hline
full uniform &
\textit{all uniform transformations} &
all start times, sources and destinations are equally likely
\\\hline\hline
time marginal &
$\mat{A}' = (\nicefrac{1}{f})\,\ones\mat{A}$ &
start times chosen from marginal distribution of start times
\\\hline
size marginal &
$\mat{B}' = (\nicefrac{1}{f})\,\ones\mat{B}$ &
flow size (bytes) is chosen from marginal distribution of sizes
\\\hline
node marginal &
$\mat{S}' = (\nicefrac{1}{f})\,\ones\mat{S} \quad
 \mat{D}' = (\nicefrac{1}{f})\,\ones\mat{D}$ &
source and dest. chosen marginally, independent of other properties
\\\hline
packet marginal &
$\mat{Z}' = (\nicefrac{1}{f})\,\ones\mat{Z} \quad
 \mat{V}' = (\nicefrac{1}{f})\,\ones\mat{V}$ &
packet behavior is variable bit-rate, marginal across all flows
\\\hline
full marginal &
\textit{all marginal transformations} &
applies all the marginality assumptions of the above four models
\\\hline\hline
source conditional &
$\mat{F}' = \rStoch(\trans{\mat{S}}\mat{S})\,\mat{F}$ &
flow behaviors are aggregated on a per source-node basis
\\\hline
dest. conditional &
$\mat{F}' = \rStoch(\trans{\mat{D}}\mat{D})\,\mat{F}$ &
flow behaviors are aggregated on a per destination-node basis
\\\hline
% mixed conditional &
% $\mat{F}' = \nicefrac{1}{2}\,(
%               \rStoch(\trans{\mat{S}}\mat{S}) +
%               \rStoch(\trans{\mat{D}}\mat{D})
%             )\,\mat{F}$ &
% flow behaviors are aggregated on a mixed source/destination basis
% \\\hline
\end{tabular}
\caption{Matrix-based traffic models used in paired differential simulation experiments.}
\label{tab:traffic-models}
\end{center}
\vspace{-1em}
\end{table*}
